---
title: "literature_master"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Dependencies
library(dagitty)
library(rethinking)


```


## Template

The first part of this project involves a broad literature search and distillation process. Using the template below we summarize relevant literature.

The three broad categories of interest that a paper may relate to are:

- It is a obvious that trade comes about as a result of costs and benefits, but what are these specifically? Particularly in relation to ecology and culture [code 1]

- What is the relationship/process between the division of labour and trade? [code 2]

- What are the conditions (ecological but perhaps also social), that favour trade over other forms of spatio-temporal averaging (mobility, storage, etc.) [code 3]


Going forward, the researcher should copy and paste the template in the literature section and fill in all the relevant blocks

----------------------------template------------------------------------------------------------------------------------

# Paper citation


# Summary sentence 


# Which key question is it related to and how


# Type of research (empirical, model, review)


# Model present?


# If yes, sketch, and note equations


```{}

```


# DAG of formal OR verbal model

```{r}

```


# Notes & issues



-----------------------end-template---------------------------------------------------------------------------------------

##Literature

# Paper citation

Gavrilets, S. (2010). Rapid transition towards the division of labor via evolution of developmental plasticity. PLoS Computational Biology, 6(6), 1–10. https://doi.org/10.1371/journal.pcbi.1000805


# Summary sentence 
Using functional division of cells under multicellularity as a model, Gavrilets shows that functional division can evolve easily and in not so many generations through developmental plasticity


# Which key question is it related to and how
2 - the paper deliberates on the question of how a division of functions between cells can arise, that is, under what conditions. The system under question is division under multicellularity.

# Type of research (empirical, model, review)
modeling

# Model present?
yes

# If yes, sketch, and note equations
```{}
#"To capture the fundamental trade-offs between cells division and locomotion capabilities  I postulate indirect negative effects of X on viability and ofY on fertility." a is streght of selection, b is stregth of tradeoffs

#fertility
f <- X^a * (1-Y)^b

#viability
v <- Y^a * (1-X)^b

#viability of colony is average viability of cells
V <- Sum(v[i]/S)

#beverton-holt model for viability selection
#N = total number of colonies
#K = carrying capacity
[1+(b-1)*(N/KV) ]^-1

#mutation, resulting in approx d/2 mutated cells per colony
#gene regulation, through two suppressor genes that affect fertility and viability
#reduction of viability and fertility happens through gaussian functions, I'm not sure how to rewrite these here


#results
#"In general, analytical and numerical results show that increasing the strength of selection a, the strength of trade-offs b, and decreasing the colony size S result in decreasing both fitness components and the population size"



```


# DAG of formal OR verbal model
```{r}
#note in this case the verbal model stems from the model analysis 

# selection on major loci -> evolution of developmental plasticity -> suppression of complementary functions in different subsets of population
#under conditions: strong trade-off between functions, high mutation rates, low costs to dev. plasticity, some sort of external cue/environmental change to set things in motion

#DAG

gavrilets_dag <- dagitty( "dag {
          selection_loci -> ev_dev_plast
          ev_dev_plast -> supp_comp_func
}")

coordinates(gavrilets_dag) <- list( x = c(selection_loci = 1, ev_dev_plast = 2, supp_comp_func = 3),
                             y = c(selection_loci= 1, ev_dev_plast = 1, supp_comp_func = 1))

plot(gavrilets_dag)
```

# Notes & issues
- interesting point in the discussion: cell types increase with number of cells because the number of cells changes the fitness landscape and thus division of labour/specialisation is necessary for optimization. Would this link to some arguments made about population size and trade? It also could be reformulated as a niche construction argument where a growing population changes the environment such that division of labour is necessary. This would be a neat feedback loop to model. 
- the model is not really general, it is "biologicall realistic" and tuned to the case of multicellularity





