---
title: "literature_master"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Dependencies
library(dagitty)
library(rethinking)


```


## Template

The first part of this project involves a broad literature search and distillation process. Using the template below we summarize relevant literature.

The three broad categories of interest that a paper may relate to are:

- It is a obvious that trade comes about as a result of costs and benefits, but what are these specifically? Particularly in relation to ecology and culture [code 1]

- What is the relationship/process between the division of labour and trade? [code 2]

- What are the conditions (ecological but perhaps also social), that favour trade over other forms of spatio-temporal averaging (mobility, storage, etc.) [code 3]

----------------------------template------------------------------------------------------------------------------------

Paper citation


Summary sentence 


Which key question is it related to and how


Type of research (empirical, model, review)


Model present?


If yes, sketch, and note euqations


```{}

```


DAG of formal OR verbal model

```{r}

```


Notes



-----------------------end-template---------------------------------------------------------------------------------------






